Design and Implementation of\\Anglican Probabilistic Programming Language

### 2016-09-02 slides/slides.tex
as presented

\begin{frame}{Why functional?}
    We want a functional language because an inference algorithm
    controls the execution:
    \begin{itemize}
        \item A program is run many (often many hundreds of
            thousands) of times (with almost any algorithm).
        \item A program must be partially re-executed multiple
            times from different positions (particle methods).
        \item We want to reason about the distribution defined
            by the program.
    \end{itemize}
\end{frame}

@@

\begin{frame}{Anglican and Clojure}
    One language on top of (or besides) another:
    \begin{itemize}
        \item Interpeter.
        \item Source-to-source compiler.
        \item Integrated language. $\checkmark$
    \end{itemize}
    \pause
    \bigskip
    Integrated language
    \begin{itemize}
        \item either extends the syntax of the host language;
        \item or changes the semantics of the host language
            constructs $\checkmark$.
    \end{itemize}
    \pause
    \bigskip
    Anglican is 
    \begin{itemize}
        \item Integrated with Clojure.
        \item Shares syntax.
        \item Alters operational semantics.
    \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{Macro-based compilation}
    Anglican code macro-compiled into Clojure, in CPS:
    \begin{minipage}{0.48\textwidth}
\begin{minted}[linenos, fontsize=\scriptsize]{clojure}
(loop [data data]
  (if (seq data)
    (let [[x & data] data]
      (observe (gamma a b) x)
      (recur data))
    (predict :a a)))
\end{minted}
    \end{minipage}
    \begin{minipage}{0.44\textwidth}
    \vspace{2em}
\begin{minted}[linenos, fontsize=\scriptsize]{clojure}
(fn loop [C23151 $state data]
   (if (seq data)
     (let [[x & data] data]
       (->observe 'O23153 (gamma a b) x
         (fn do23152 [_ $state]
           (loop C23151 $state data))
         $state))
     (fn []
       (C23151
         nil
         (add-predict $state :a a)))))
\end{minted}
    \end{minipage}
	\bigskip

>>>>

\begin{frame}{Why functional?}
    We want a functional language because an inference algorithm
    controls the execution:
    \begin{itemize}
        \item A program is run many (often many hundreds of
            thousands) of times (with almost any algorithm).
        \item A program must be partially re-executed multiple
            times from different positions (particle methods).
        \item We want to reason about the distribution defined
            by the program.
    \end{itemize}
	\bigskip
	We need
	\begin{itemize}
		\item First-class functions.
		\item No side effects.
	\end{itemize}
\end{frame}

@@

\begin{frame}{Anglican and Clojure}
    One language on top of (or besides) another:
    \begin{itemize}
        \item Interpeter.
        \item Source-to-source compiler.
        \item Integrated language. $\checkmark$
    \end{itemize}
    \pause
    \bigskip
    Integrated language
    \begin{itemize}
        \item either extends the syntax of the host language;
        \item or changes the semantics of the host language
            constructs. $\checkmark$
    \end{itemize}
    \pause
    \bigskip
    Anglican is 
    \begin{itemize}
        \item Integrated with Clojure.
        \item Shares syntax.
        \item Alters operational semantics.
    \end{itemize}
\end{frame}

@@

\begin{frame}[fragile]{Macro-based compilation}
    Anglican code macro-compiled into Clojure, in CPS:
    \begin{minipage}{0.48\textwidth}
\begin{minted}[linenos, fontsize=\scriptsize]{clojure}
(loop [data data]
  (if (seq data)
    (let [[x & data] data]
      (observe (gamma a b) x)
      (recur data))
    (predict :a a)))
\end{minted}
    \end{minipage}
    \begin{minipage}{0.44\textwidth}
    \vspace{2em}
\begin{minted}[linenos, fontsize=\scriptsize]{clojure}
((fn loop [C23151 $state data]
   (if (seq data)
     (let [[x & data] data]
       (->observe 'O23153 (gamma a b) x
         (fn do23152 [_ $state]
           (loop C23151 $state data))
         $state))
     (fn []
       (C23151
         nil
         (add-predict $state :a a)))))
  cont $state data)
\end{minted}
    \end{minipage}
	\bigskip
